Normalized expressions

### 2021-02-26 analysis/normalized.Rmd
Generate notebook for each dataset
Declutter normalized.Rmd

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw
read_csv(static_path) %>% semi_join(C_raw, by = "package") -> P

@@

```{r}
by_src_ref %>% datatable()
```

>>>>

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw
#read_csv(static_path) %>% semi_join(C_raw, by = "package") -> P

@@

```{r}
by_src_ref %>% arrange(desc(n_resolved)) %>% datatable()
```
